---
title: "R Markdown Demo"
author: "Yihui Xie"
date: '2020-11-10'
slug: r-markdown-demo
features: [+sticky_menu]
toc-title: Outline
bibliography: packages.bib
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(fig.retina = 2, dev = if (xfun::loadable('svglite')) 'svglite' else 'svg')
```

## Floats

### Full-width figures

Use a fenced `Div` with the class `fullwidth`, e.g.,

```` {.md}
::: {.fullwidth}
Any Markdown content or code blocks here.

```{r, echo=FALSE, fig.dim=c(14, 4)}`r ''`
plot(sunspots)
```
:::
````

::: {.fullwidth}
```{r, sunspots, echo=FALSE, fig.dim=c(14, 4), fig.cap='Monthly mean relative sunspot numbers from 1749 to 1983. Collected at Swiss Federal Observatory, Zurich until 1960, then Tokyo Astronomical Observatory.'}
par(mar = c(4, 4, .1, .1), bg = 'lightgoldenrodyellow', fg = 'red', las = 1)
plot(sunspots, col = 'red', panel.first = grid())
```
:::

If you add the class `fullscroll` to the `Div`, the figure will be scrollable,
e.g.,

``` {.md}
::: {.fullwidth .fullscroll}

:::
```

::: {.fullwidth .fullscroll}
```{r, scroll, ref.label='sunspots', echo=FALSE, fig.dim=c(30, 3), fig.cap='This is a super wide figure that you need to scroll to view it fully.'}
```
:::

### Embedded figures

You can embed any elements (typically figures) that span into the page margin.
Use a fenced `Div` with the class `embed-left` or `embed-right`, e.g.,

::: {.embed-right}
```{r, embed-plot, echo=FALSE, fig.dim=c(5, 2.5), fig.cap='This is a figure embedded on the right.'}
par(mar = c(3, 3, .3, .3), las = 1, cex.axis = .8, cex.lab = .8, mgp = c(2, .5, 0))
plot(cars, pch = 19, col = 'steelblue', panel.first = grid())
```
:::

```` {.md}
::: {.embed-right}

Here is a special figure.

```{r}`r ''`
plot(cars)
```
:::
````

If you want to embed a table, that will be okay, too. Really, you can embed
anything.

```` {.md}
::: {.embed-left}
```{r, echo=FALSE}`r ''`
knitr::kable(head(mtcars), caption = 'An example dataset.')
```
:::
````

::: {.embed-left}
```{r, echo=FALSE}
knitr::kable(head(mtcars), caption = 'An example dataset.')
```
:::

Now I have generate some text to fill the space on the right:
`r paste(rep('hold my beer', 60), collapse = ' ')`.

## Text elements

### Table of contents

TOC should be automatically generated unless it is disabled via
`features: [-toc]` in YAML. To define the TOC title, use the `toc-title` field
in YAML.

### Section numbers

Sections should be automatically numbered unless Pandoc has already numbered
them,[^1] or the feature is disabled via `features: [-number_sections]`.

[^1]: Apply the option `number_sections: true` to the output format
    `blogdown::html_page` in YAML.

### Footnotes

Footnotes should be automatically moved to the right margin,[^2] unless the
feature is disabled via `features: [-sidenotes]`.

[^2]: For example, this is a footnote.

### Sidenotes

Sidenotes can be generated via a div with classes `side` and `side-left` or
`side-right`. You can use either the HTML syntax `<div class="side side-left">`
or Pandoc's fenced `Div`, e.g.,

::: {.side .side-right}
This is a **sidenote** on the right side when the window is wider than 1280px.
:::

``` {.md}
::: {.side .side-right}
This is a **sidenote** on the right.
:::
```

### Citations

Use `bibliography` or `references` in YAML to include the bibliography database,
and use `@` to cite items, e.g., `@R-base` generates @R-base.

```{r}
knitr::write_bib('base', 'packages.bib')
```

As you can see above, we generated a `.bib` database with `knitr::write_bib()`.

Citation entries are displayed in the right margin by default like footnotes. To
disable this behavior, set `features: [-sidenotes]` in YAML.
